The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-12 draft/ms.tex
Minor fix on table refs.
Modify ref for SHK and RHK fields in table.

%------------------------------------------------------------------------------
\subsection{Removed Fields}

@@

MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata & W11 \\

@@

Archive database & EAURL & \ref{sec:disc} \\

@@

SHK\dotfill & Float & Mount Wilson Ca {\sc{II}} $S$-value & \nodata & \ref{sec:stellarmag} \\
RHK\dotfill & Float & Chromospheric activity of star as $\log{R'_{HK}}$ & \nodata & W11 \\

>>>>

%------------------------------------------------------------------------------
\subsection{Removed Fields}\label{sec:removed}

@@

MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata & \ref{sec:disc} \\

@@

Archive database & EAURL & \ref{sec:removed} \\

@@

SHK\dotfill & Float & Mount Wilson Ca {\sc{II}} $S$-value & \nodata & \ref{sec:ref} \\
RHK\dotfill & Float & Chromospheric activity of star as $\log{R'_{HK}}$ & \nodata & \ref{sec:ref} \\
